
% Many thanks to Andrew West for writing most of this file
% Main LaTeX file for CIS400/401 Project Proposal Specification
%
% Once built and in PDF form this document outlines the format of a
% project proposal. However, in raw (.tex) form, we also try to
% comment on some basic LaTeX technique. This is not intended to be a
% LaTeX tutorial, instead just (1) a use-case thereof, and (2) a
% template for your own writing.

% Ordinarily we'd begin by specifying some broad document properties
% like font-size, page-size, margins, etc. -- We have done this (and
% much more) for you by creating a 'style file', which the
% 'documentclass' command references.
\documentclass{sig-alternate}

% These 'usepackage' commands are a way of importing additional LaTeX
% styles and formattings that aren't part of the 'standard library'
\usepackage{mdwlist}
\usepackage{url}

\begin{document}
\nocite{*}
% We setup the parameters to our title header before 'making' it. Note
% that your proposals should have actual titles, not the generic one
% we have here.
\title{Electronic Knee Wrap for Injury Prediction}
\subtitle{Dept. of CIS - Senior Design 2013-2014\thanks{Advisor: LeAnn Dourte (dourte@seas.upenn.edu), Insup Lee (lee@cis.upenn.edu)}}
\numberofauthors{4}
\author{
\alignauthor Alex Yau \\ \email{ayau@sas.upenn.edu} \\ Univ. of Pennsylvania \\ Philadelphia, PA
\alignauthor Jacy Clare \\ \email{jclare@sas.upenn.edu} \\ Univ. of Pennsylvania \\ Philadelphia, PA
\and
\alignauthor Jeffrey Shih \\ \email{jeshih@sas.upenn.edu} \\ Univ. of Pennsylvania \\ Philadelphia, PA
\alignauthor Kunal Mahajan \\ \email{mkunal@seas.upenn.edu} \\ Univ. of Pennsylvania \\ Philadelphia, PA}
\date{\today}
\maketitle

% Next we write out our abstract -- generally a two paragraph maximum,
% executive summary of the motivation and contributions of the work.
\begin{abstract}

  \textit{This research focuses on creating an electronic knee wrap for athletes to wear in order to monitor the motion of their knees to reduce the risk of suffering an Anterior Cruciate Ligament (ACL) injury or reinjury. While significant research has been conducted for identifying the factors responsible for an ACL injury, there is a need to quantitatively determine an athlete's risk of suffering the injury in order to determine if an athlete is fit to return to sports. To this end, this reserach explores the opportunity to mount a high performance, small area circuit on a knee wrap. A set of factors that are important to the calculation of an athelete's risk of a future knee injury, such as knee acceleration, knee orientation and valgus forces, is collected from the knee wrap in real time. In addition, this knee wrap will also be multi-purpose, allowing both doctors to monitor an athelete's recovery remotely and coaches to observe an athelete's performance on the field.}

  \textit{The design incorporates microcontrollers, inertial measurement units and wireless module mounted on the knee wrap. In order for the therapists and physicians to interact with the data, a server and a front-end web interface is implemented to display the data.}

\end{abstract}

% Then we proceed into the body of the report itself. The effect of
% the 'section' command is obvious, but also notice 'label'. Its good
% practice to label every (sub)-section, graph, equation etc. -- this
% gives us a way to dynamically reference it later in the text via the
% 'ref' command.
\section{Introduction}
\label{sec:intro}
ACL ruptures are one of the most common injuries in sport and very expensive to treat. There are approximately 175, 000 primary ACL reconstruction surgeries performed annually in the USA with an estimated cost of over \$2 billion US~\cite{yu2007mechanisms}. This is followed by a lengthy rehabilitation period. Even then, over a quarter of patients reinjure their ACL~\cite{stevenson1998gender}. These injuries also cause early-onset of osteoarthritis for numerous people between the ages of 30 and 50, and related injuries such as ACL tear in the other leg.~\cite{2d7e8810e30d11dd990c000ea68e967b}

An ACL injury can have an immense impact on an athelete's career and quality of life. Because of this, monitoring and reducing the risk of ACL injuries is exceptionally valuable and important. This research proposes the use of an electronic knee wrap (eKwip), to predict and prevent ACL injuries in both healthy athletes and injured patients. By monitoring the angles, orientation and movements of the knee of the wearer, eKwip is able to capture the important factors that are responsible for an ACL injury and allows doctors to observe the movements of the athelete and give recommendations to correct his running or landing posture to reduce the risk of future injuries.  To encourage adoption of such a knee wrap, eKwip is designed to be unobtrusive and flexible, unlike the current mechanical braces on the market.

eKwip is designed to be mobile and allows the wearer to monitor his or her knee performance throughout the day to decrease the chance of future injury. It also allows physical therapist to easily observe and assess the performance of injured patients remotely. With eKwip, the aim is to reduce the rate of ACL injuries in both healthy athletes and injured patients.

eKwip utilizes various factors that have been demonstrated to cause the injury such as accelerations and angles. eKwip currently only acts as a system that collects information from the knee of the wearer and transmits to the computer of the doctors in the clinic, or coaches on the field. Although the type of information collected is tailored towards understanding the risk of ACL injury, the benefits of monitoring the knee is not restricted to just that. Additional rehab applications of eKwip may include monitoring patients post operation, collecting information on Stiff Knee, and tracking total joint cycles on older patients. Given the collected information, the doctors can then interpret the performance and health of the patients and give corresponding recommendations.

eKwip consist of a microcontroller that receives knee acceleration and orientation angles from its sensors. Using a wireless module, this data is quickly transmitted to the server, which calibrates the angles and acceleration, and displays them on the website in a user friendly format.

Sec. 2 reviews knee anatomy, including the major causes of ACL injuries and the performance requirement of eKwip. Then, Sec. 3 discusses the prior work in ACL detection and the common rehabilation procedures used in the industry for measuring the strength of the ACL. Sec. 4 illustrates the basic idea of eKwip with the model diagram. Sec. 5 describes the technical implementation of eKwip in detail. As real-time analysis is a necessary component, Sec. 6 describes the performance of the system with respect to requirements and how the system improved over time as well as the sample results collected from eKwip. Sec. 7 details the future work that can be done to improve eKwip and Sec. 8 contains a brief discussion of potential ethical issues of the wrap. Throughout the paper, we focus on latency and unobtrusiveness of the wrap.

% The header of this document might have been a little intimidatating
% to beginners. Notice once you are in the body of the document,
% however, LaTeX commands are minimal and 'normal text' is frequent.
\section{Background}
\label{sec:background}
\input{sections/background.tex}

\section{Related Work}
\label{sec:related_work}
\input{sections/related.tex}

\section{System Model}
\label{sec:system_model}
\input{sections/model.tex}

\section{System Implementation}
\label{sec:system_implementation}
\input{sections/implementation.tex}

\section{System Performance}
\label{sec:system_performance}
\input{sections/performance.tex}

\section{Results}
\label{sec:results}
\input{sections/results.tex}

\section{Future Work}
\label{sec:future_work}
\input{sections/futurework.tex}

\section{Ethics}
\label{sec:ethics}
The rapid increase in the acceptance of wearable technology will create numerous problems. In the current form of the wrap can cause physical discomfort for the user. For instance, the microcontroller, soldered on the PCB board, has pins sticking out. Those pins can cause friction during use and leave the user with scratches and injuries on his femur and tibia. To solve this problem, the wrap can have a custom-made PCB board that can mount the microcontrollers, IMUs and the wifly module without the pins coming in any contact with the skin.

In addition to physical injuries, it is possible that the wrap can create financial problems for the athletes. If all the athletes are mandated to use the wrap, the manufacturer can put a ridiculous price tag that will economically burden the athletes. Medical devices are highly regulated by FDA. For approval, the company has to go through 7-10 years of extensive testing while spending millions of dollars. While this would justify the price tag, it would nevertheless reduce the accessibility of the wrap for everyone other than athletes. One way to reduce the price tag would be to cover the cost of the wrap under insurance. This strategy would raise the insurance prices but they won’t increase significantly enough than standalone purchase as the cost is distributed by the insurance companies among lot of people.

% We next move onto the bibliography.
\bibliographystyle{plain} % Please do not change the bib-style
\bibliography{sections/references}  % Just the *.BIB filename

\end{document}

