
% Many thanks to Andrew West for writing most of this file
% Main LaTeX file for CIS400/401 Project Proposal Specification
%
% Once built and in PDF form this document outlines the format of a
% project proposal. However, in raw (.tex) form, we also try to
% comment on some basic LaTeX technique. This is not intended to be a
% LaTeX tutorial, instead just (1) a use-case thereof, and (2) a
% template for your own writing.

% Ordinarily we'd begin by specifying some broad document properties
% like font-size, page-size, margins, etc. -- We have done this (and
% much more) for you by creating a 'style file', which the
% 'documentclass' command references.
\documentclass{sig-alternate}

% These 'usepackage' commands are a way of importing additional LaTeX
% styles and formattings that aren't part of the 'standard library'
\usepackage{mdwlist}
\usepackage{url}

\begin{document}
\nocite{*}
% We setup the parameters to our title header before 'making' it. Note
% that your proposals should have actual titles, not the generic one
% we have here.
\title{Electronic Knee Wrap for Injury Prediction}
\subtitle{Dept. of CIS - Senior Design 2013-2014\thanks{Advisor: LeAnn Dourte (dourte@seas.upenn.edu), Insup Lee (lee@cis.upenn.edu)}}
\numberofauthors{4}
\author{
\alignauthor Alex Yau \\ \email{ayau@sas.upenn.edu} \\ Univ. of Pennsylvania \\ Philadelphia, PA
\alignauthor Jacy Clare \\ \email{jclare@sas.upenn.edu} \\ Univ. of Pennsylvania \\ Philadelphia, PA
\and
\alignauthor Jeffrey Shih \\ \email{jeshih@sas.upenn.edu} \\ Univ. of Pennsylvania \\ Philadelphia, PA
\alignauthor Kunal Mahajan \\ \email{mkunal@seas.upenn.edu} \\ Univ. of Pennsylvania \\ Philadelphia, PA}
\date{\today}
\maketitle

% Next we write out our abstract -- generally a two paragraph maximum,
% executive summary of the motivation and contributions of the work.
\begin{abstract}

  \textit{Anterior Cruciate Ligament (ACL) injuries are among the most common injuries in sports. While significant research has been conducted for identifying the factors responsible, there is a need to quantitatively determine an athlete's risk of suffering the injury in real time. To this end, we explore the opportunity to mount a high performance, small area circuit on a knee wrap. We integrate a set of factors such as knee acceleration, knee orientation and valgus forces for computing the risk percentage of an athlete in real time. In addition, this knee wrap will also be multi-purpose, allowing both doctors to predict injuries and athletes prevent injuries on the field.}

  \textit{The design incorporates microcontrollers, inertial measurement units and wireless module mounted on the knee wrap. In order for the therapists and physicians to interact with the data, we have implemented a server and are using a website to display the data. We are able to show that the sensors measure accurate data at (TODO Hz) frequency, successfully transmit to the server and display the data.}

\end{abstract}

\begin{keywords}
	Anterior Cruciate Ligament (ACL),  Knee Flexion angle, Deceleration, Knee Injury Risk Index (KIRI)
\end{keywords}

% Then we proceed into the body of the report itself. The effect of
% the 'section' command is obvious, but also notice 'label'. Its good
% practice to label every (sub)-section, graph, equation etc. -- this
% gives us a way to dynamically reference it later in the text via the
% 'ref' command.
\section{Introduction}
\label{sec:intro}
ACL ruptures are one of the most common injuries in sport and very expensive to treat.There are approximately 175, 000 primary ACL reconstruction surgeries performed annually in the USA with an estimated cost of over \$2 billion US \cite{yu2007mechanisms}. This is followed by a lengthy rehabilitation period. Even then, over a quarter of patients reinjure their ACL \cite{stevenson1998gender}. These injuries also cause early-onset of osteoarthritis for numerous people between the ages of 30 and 50, and related injuries such as ACL tear in the other leg. (TODO cite Lohmander et al)

An ACL injury can have an immense impact on an athelete's career and quality of life. Because of this, preventing ACL injuries is exceptionally valuable and important. We propose the use of an electronic knee wrap (eKwip), to predict and prevent ACL injuries in both healthy athletes and injured patients. By monitoring the angles, orientation and movements of the knee of the wearer, eKwip is able to predict when an injury is imminent. We propose to create a prevention mechanism to cushion knee and prevent the knee from bending at angles that may cause an ACL rupture. This mechanism will be triggered in case of imminent danger. To encourage adoption of such a knee wrap, eKwip is designed to be unobtrusive and flexible, unlike the current mechanical braces on the market.

eKwip allows the wearer to monitor his or her knee performance and risk of injury throughout the day to decrease the chance of future injury. It also allows physical therapist to easily observe and assess the performance of injured patients remotely. With eKwip, the aim is to reduce the rate of ACL injuries in both healthy athletes and injured patients.

eKwip utilizes various factors that have been demonstrated to cause the injury such as accelerations and angles. It integrates these factors with machine learning algorithm to accurately calculate the risk by adapting to the athlete's physical characteristics such as flexiblity and normal range of knee movement. Currently, the microcontroller (Mbed) receive knee acceleration and orientation angles from the sensors. Using a wireless module, this data is quickly transmitted to the server, which calibrates the angles and acceleration, and displays them on the website in a user friendly format.

Sec.2 reviews knee anatomy, including the major causes of ACL injuries and the performance requirement of eKwip. Then, we review the prior work in ACL detection and the common rehabilation procedures used in the industry for measuring the strength of the ACL in Sec.3. Sec.4 illustrates the basic idea of eKwip with the model diagram. Sec.5 describes the technical implementation of eKwip in detail. As real-time analysis is a necessary component, Sec.6 describes the performance of the system with respect to requirements and how we improved the system over time. Sec.7 details our remaining work that involves implementation of KIRI algorithm, machine learning implementation, and testing and validating the system. Throughout the paper, we focus on latency and unobtrusiveness of the wrap.

% The header of this document might have been a little intimidatating
% to beginners. Notice once you are in the body of the document,
% however, LaTeX commands are minimal and 'normal text' is frequent.
\section{Background}
\label{sec:background}
\input{sections/background.tex}

\section{Related Work}
\label{sec:related_work}
\input{sections/related.tex}

\section{System Model}
\label{sec:system_model}
\input{sections/model.tex}

\section{System Implementation}
\label{sec:system_implementation}
\input{sections/implementation.tex}

\section{System Performance}
\label{sec:system_performance}
\input{sections/performance.tex}

\section{Remaining Work}
\label{sec:remaining_work}
\input{sections/remainingWork.tex}

% We next move onto the bibliography.
\bibliographystyle{plain} % Please do not change the bib-style
\bibliography{sections/references}  % Just the *.BIB filename

\end{document}

